Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-16 prop.tex
prop.tex \appendix Starting...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}

@@

\end{comment}
\printbibliography 
\end{document}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}

@@

\end{comment}
\printbibliography

\appendix

\section{Increasing the Measurement Resource}

In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
although quantum IVPMs have empty cores, we might think that the probability
measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
the probability measure $\bar{\mu}$ might be induced by the state
$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
In example~\ref{ex:three-dimensional-4-value}, the probability measure
$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
Notice that the set of 1-dimensional projectors mapping to impossible,
$\bar{\mu}^{-1}\left(\imposs\right)=\left\{ \ket{\phi}\in\mathbb{C}^{3}\middle|\bar{\mu}(\proj{\phi})=\imposs\right\} $
provides a appealing way to suggest a possible state inducing $\bar{\mu}$.
Since for any two states~$\ket{\phi_{0}},\ket{\phi_{1}}\in\bar{\mu}^{-1}\left(\imposs\right)$,
we have $\bar{\mu}(\proj{\phi_{0}})=\bar{\mu}(\proj{\phi_{1}})=\imposs$
so that $\bar{\mu}$ might be induced by the state $\ket{\phi_{0}}\times\ket{\phi_{1}}$\footnote{\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
of $\mathbb{C}^{3}$. Although this might be just tedious details
in this approach, still need to verify carefully.}}.

\section{Subset of Computing Events}

\footnote{\yutsung{The Kochen-Specker theorem is about assigning definitely
value to observables such that the values of commuting observables
are consistent; the Bell theorem is about entangled states in different
locations. If our results are more related to commuting observables,
it is more related to the Kochen-Specker theorem than the Bell theorem...}}

\end{document}
